An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-24 Revision/response.tex

%%%%%%%%%%%%%%%%%%%%%% R4 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{metarevision}
		\textit{Instead of using the point ID, run experiments with meaningful attributes for RF-NN search on datasets (Deep, YT-Audio, WIT).}
	\end{metarevision}
}

\noindent
\textbf{Response:} 
Thank you for your suggestion. Using IDs as attributes for range filtering is a prevalent method in current range filtering algorithm evaluations, which indeed has considerable limitations. To address this issue, we add two datasets that use real attributes:

\textbf{YT-Audio-Real dataset:} For this dataset, we utilize the URLs provided by the YouTube8M dataset to crawl corresponding video categories and view counts as real attributes, using \textbf{video categories as attributes for attribute filtering experiments} and \textbf{view counts as attributes for range filtering experiments}, respectively.

\textbf{WIT-Real dataset:} We use the \texttt{clip-vit-base-patch32} model to encode the \texttt{page\_title} field from the WIT dataset into vectors, and extract the language type and the length of the \texttt{context\_page\_}
\texttt{description} field as real attributes, applying them in both attribute filtering and range filtering experiments.

@@

To address this crucial issue and enhance the real-world relevance of our evaluation, we have added two new real-world datasets with genuine attributes to our attribute filtering and range query experiments, as detailed in MetaReview R3.

We have revised the manuscript accordingly. (Please see page 7, Section 4.2.1, and the "Single-Attribute Building and Single-Attribute Query" subsection of Section 4.2.2 on page 8, highlighted in blue in the revised manuscript.) Furthermore, it should be noted that, in the "Single-Attribute Building and Single-Attribute Query" subsection of Section 4.2.2 on page 8, due to space constraints, we have removed two previous datasets (Audio and GloVe), as Audio is relatively small-scale, and GloVe's scale is similar to SIFT1M while its LID is similar to GIST1M.

%%%%%%%%%%%%%%%%%%%%%% W2 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{weakness}
		\textit{All experiments were conducted on the same server mentioned in Section 4.1.3.
			However, in practice, server providers may use other hardware settings (with other processors and RAM).
			Would the server setting affect the relative ordering of methods in experiments?
			For example, if Intel Xeon processor is used, would there be any change of the top 3 methods in Figures 4,5,7,8?
			Would the CPU cache size affect the top 3 methods in those figures?}
	\end{weakness}
}

\noindent
\textbf{Response:} 
Thank you for your suggestion. We have added relevant experiments conducted on different servers in Section 4.2.4. Please refer to the response MR.R4 for more details.
%%%%%%%%%%%%%%%%%%%%%% W3 %%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%% W1 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{weakness}
		\textit{Scalability experiments are missing; largest dataset is 10M; some pitfalls will only show at large scale.}
	\end{weakness}
}

\noindent
\textbf{Response:} 
Thank you for your suggestion. We add experiments on the Deep100M dataset in Section 4.2.4 and Section 4.3.4, and we observe some pitfalls. For more details, please refer to our response to Meta Review R7.

%%%%%%%%%%%%%%%%%%%%%% W2 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{weakness}
		\textit{The explanations provided with the performance results are not as insightful as they need to be to point out the pros and cons of the different algorithms.}
	\end{weakness}
}

\noindent
\textbf{Response:} 
Thank you for pointing this out. We agree that the initial explanations accompanying the performance results were not sufficiently detailed in highlighting the strengths and weaknesses of the compared algorithms. We have conducted a more in-depth analysis of the reasons behind certain behaviors observed in the experimental results. The specific revisions are as follows:
%下面写每个修改过的理由
%%%%%%%%%%%%%%%%%%%%%% W3 %%%%%%%%%%%%%%%%%%%%%%

### 2025-07-24 VLDB2026/main.tex
Update main.tex

		\centering
		%	 \setlength{\abovecaptionskip}{0cm}
		%	\setlength{\belowcaptionskip}{0.1cm}
		\footnotesize{
			\begin{minipage}{\linewidth}
				\vspace{0.1cm}
				Win: WinFilter, Filtered: Filtered-DiskANN, Stitched: StitchedVamana. 
				\textsuperscript{B} Pre-filtering, 
				\textsuperscript{C} Simultaneous filtering, 
				\textsuperscript{Y} Support, 
				\textsuperscript{N} Unsupport. 
				\textit{AND} and \textit{OR} indicate whether the algorithm supports the corresponding logical operations.
				\textit{Flexible Attributes} indicates whether the number of query attributes can differ from the number of attributes used during index construction. 
				\textit{Complex Boolean} indicates if the algorithm supports complex expressions, such as using the NOT operator or nested logic with parentheses.
				\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
				\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
				\textit{Disk Support} indicates whether the algorithm supports disk storage.
				\textit{Base} indicates the foundational ANN algorithm for the hybrid query method.
		\end{minipage}}

@@

	To investigate the performance of different attribute filtering algorithms during index construction, we evaluate \textcolor{orange}{4} key metrics in the single-attribute scenario: index construction time, index size, \textcolor{orange}{build peak memory and search peak memory}. Notably, PASE on GIST1M and Enron is omitted, as it supports only data with dimensionality less than 512. \textcolor{orange}{Except for algorithms that only support single-threaded construction, all other algorithms are built using 32 threads on the 6 datasets shown in the left figure, and 64 threads on the large-scale Deep100M dataset.}

@@

\textit{\textbf{Index construction time.}}
\textcolor{orange}{Among the six regular-scale datasets shown in the left part of Figure~\ref{fig:build_time_comparison_query1}, the ones with longer build times are mainly PASE, VBASE, and ACORN. PASE and VBASE only support single-threaded builds, and PASE is the slowest to build because its on-demand loading and caching strategies frequently trigger disk I/O and page scheduling, which seriously affects efficiency; VBASE uses full-memory builds and is relatively faster. ACORN-$\gamma$  has a large computational overhead because it needs to expand the neighbor list and evaluate a large number of candidates. The build time on some datasets even exceeds that of single-threaded VBASE. }

\textcolor{orange}{On large-scale dataset Deep100M, besides the three methods already mentioned with long build times, we also find that graph-based algorithms using pruning strategies (such as FilteredDiskANN and UNG) exhibit significantly increased construction time, especially when the pruning is complex and extensive, leading to higher computational overhead. In contrast, the construction time of IVF-based algorithms grows much more slowly with dataset size, thanks to their shard-based design and high parallel efficiency, making them more scalable and advantageous in large-scale scenarios.}

%ACORN-1 achieves the fastest index construction. This efficiency stems from its similarity to the original HNSW construction process and the use of a limited number of candidate neighbors.

%\textcolor{orange}{As shown in Figure~\ref{fig:build_time_comparison_query1}, in the above datasets, both PASE and VBASE are single-threaded indexing methods, with PASE having the longest construction time. The on-demand loading and caching strategy used by PASE results in frequent disk I/O and page scheduling, which significantly slow down the construction process. In contrast, VBASE uses full in-memory construction, leading to faster indexing.}
%
%
%For algorithms supporting 32-thread, ACORN-1 achieves the fastest index construction. This efficiency stems from its similarity to the original HNSW construction process and the use of a limited number of candidate neighbors. In contrast, ACORN-$\gamma$ incurs the highest index construction time, as it expands neighbor lists and evaluates a large candidate pool, leading to increased computational overhead. \textcolor{orange}{Its construction time on some datasets is even slower than that of the single-threaded VBASE.}
%
%On large dataset Deep100M, VBASE takes longer to build because it only supports single-threaded construction. The other time-consuming algorithms are all graph-based methods, which employ complex pruning strategies during construction to optimize query performance, leading to significantly increased build times.

@@

for big dataset:
%\underline{Faiss generates slightly smaller indexes due to its efficient index design}.

\textit{\textbf{Build peak memory.}}
% As shown in Figure~\ref{fig:build_memory_mb_comparison}, 
% %on small-scale datasets, all methods except NHQ exhibit low memory usage. 
% \textcolor{orange}{NHQ has the highest peak memory usage on almost all datasets.}
% This is because NHQ adopts the kgraph approach for index construction, which requires loading the entire graph data into memory and maintaining a complete graph structure, leading to relatively high memory overhead. 
% 
% On large-scale datasets, CAPS exhibits slightly lower memory usage compared to other algorithms. \textcolor{orange}{The reason is that CAPS avoids redundant storage and graph structure overhead through hierarchical partitioning and AFT, and achieves a compact, sparse and controllable index. }.
\textcolor{orange}{As shown in the Figure~\ref{fig:build_memory_mb_comparison}, the build peak memory usage is generally correlated with the sum of the index size generated by the algorithm and the dataset size. This trend holds consistently across different datasets. However, PASE breaks this pattern due to its on-demand loading strategy, resulting in peak memory usage even lower than the index size itself. For large-scale datasets, algorithms that produce larger indexes tend to cause significantly higher peak memory consumption during construction.}

\textit{\textbf{ \textcolor{orange}{Search peak memory.}}}
%  \textcolor{orange}{As shown in Figure~\ref{fig:search_memory_mb_comparison}, we can find that the peak memory usage of each algorithm during search does not differ significantly. Among them, CAPS and NHQ have relatively higher peak memory usage, while the peak memory usage of database is comparatively lower.}
\textcolor{orange}{For most algorithms, the query phase requires loading both the index and the dataset into memory, so its peak memory usage is usually comparable to that of the construction phase. However, as shown in the Figure~\ref{fig:search_memory_mb_comparison}, CAPS exhibits significantly higher peak memory during querying due to the need to dynamically maintain large candidate sets. In contrast, Milvus has lower query-time memory usage because it does not fully load the index and incurs additional metadata overhead during construction.
}

@@

		\includegraphics[width=0.95\textwidth]{figures/exp/exp_3_1.pdf}
		\caption{Effect of attribute distribution on query performance (single thread)}
		\label{fig:exp_3_1}

		\footnotesize{
		\begin{center}
			\begin{minipage}{\linewidth}
				\centering	
				\textit{Strong} : robust to attribute distribution shifts,  \textit{Weak} : sensitive to attribute distribution shifts
			\end{minipage}
		\end{center}
		}
	\end{figure*}

	\textit{\textbf{Multi-Attribute Building and Multi-Attribute Query.}}  
	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world scenarios. To evaluate algorithm performance under this setting, we construct the index using 3 uniformly distributed attributes and apply filtering on all 3 attributes simultaneously during queries. \textcolor{orange}{In this experiment, we only evaluate the algorithms that support this query scenario.}
	%	\textcolor{red}{As Filtered-DiskANN does not support the AND rule used in our multi-attribute queries, it is excluded.}
	%	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world application scenarios. To evaluate algorithm performance under such scenario, we construct the index using 3 uniformly distributed attributes and apply filtering conditions on all 3 attributes simultaneously during the query process.

	As shown in Figure~\ref{fig:exp_4_1_MultiLabel_1thread}, UNG achieves the best performance across all datasets. For IVF-based methods not specifically optimized for hybrid queries (Faiss\_IVF and Milvus), their QPS remains relatively stable as recall varies. Milvus, as a general-purpose system, exhibits comparatively poor performance.

		The IVF-based algorithm Faiss---especially when combined with HQI\_Batch---achieves moderate performance. It naturally supports pre-filtering and remains unaffected by the increasing number of attributes. In fact, filtering can reduce the effective candidate set, thereby improving search efficiency. In contrast, the IVF-based algorithm CAPS, which is optimized for hybrid queries, employs a multi-level partitioning strategy that introduces additional overhead. This overhead negatively impacts performance on small datasets. However, on large datasets, the overhead is amortized, and the advantages of attribute-aware partitioning become evident, making CAPS the second-best performer after UNG.

@@

	%	NHQ exhibits mediocre performance overall and performs particularly poorly on small datasets. It relies on fusion distance calculations. The fusion distance computation is highly sensitive to the number of attributes involved, thus impacting both efficiency and accuracy under multi-attribute filtering.
	NHQ performs moderately overall but poorly on small datasets. Its reliance on fusion distance computations makes it highly sensitive to the number of attributes, impacting both efficiency and accuracy under multi-attribute filtering.

@@

	As illustrated in Figure~\ref{fig:exp_3_1}, the evaluated algorithms exhibit varying degrees of sensitivity to attribute distribution shifts. \textcolor{cyan}{The proximity of the 4 curves in the figure reflects algorithm sensitivity to distributional variations. When the curves converge closely, the algorithm demonstrates strong resilience against attribute distribution shifts.} Specifically, ACORN, Milvus, Puck, CAPS, StitchedVamana, and UNG demonstrate strong robustness to such shifts. In contrast, Faiss, FilteredVamana, NHQ, VBASE, and PASE show notable sensitivity.

@@

\begin{figure*}[t]
	\centering

	% 1. 全局图例 (Legend) - 位置保持不变
	\includegraphics[width=0.9\textwidth]{figures/exp/attribute_legend.pdf}

	% --- 主要改动：将以下三个 subfigure 全部放在同一行 ---

	% 2. 第一部分：两张图，共用标题
	% [b]表示按底部对齐，在一行内通常比顶部对齐[t]效果好
	% 宽度从\textwidth缩小到0.32\textwidth
	\begin{subfigure}[b]{0.39\textwidth}
		\centering
		% 内部图片宽度使用\linewidth，它会自适应为容器宽度(0.32\textwidth)
		\includegraphics[width=0.495\linewidth]{figures/exp/attribute_multimodel.pdf}
		\hfill 
		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_multimodel_1.pdf}
		\caption{MultiModal}
		\label{fig:attribute-multimodal} 
	\end{subfigure}
	\hfill % 在第一部分和第二部分之间添加弹性间距
	% 3. 第二部分：两张图，共用标题
	\begin{subfigure}[b]{0.39\textwidth}
		\centering
		\includegraphics[width=0.495\linewidth]{figures/exp/attribute_85.pdf}
		\hfill
		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_71.pdf}
		\caption{Cross-Platform}
		\label{fig:attribute-cross-platform}
	\end{subfigure}
	\hfill % 在第二部分和第三部分之间添加弹性间距
	% 4. 第三部分：只有一张图
	\begin{subfigure}[b]{0.203\textwidth}
		\centering
		% !!! 注意：这是一个占位符，请替换成您自己的第五张图 !!!
		\includegraphics[width=0.96\linewidth]{figures/exp/attribute_100M.pdf} 
		\caption{Dig Dataset}
		\label{fig:attribute big dataset}
	\end{subfigure}

	% 5. 全局总标题
	\caption{\textcolor{violet}TrinityExtension——Attribution}
	\label{fig:TrinityExtension——Attribution_main}
\end{figure*}

@@

% 使用 figure* 环境来实现图片横跨双栏
% 使用 figure* 环境来实现图片横跨双栏

@@

\begin{figure*}[t]
	\centering

	% 1. 全局图例 (Legend) - 位置保持不变
	\includegraphics[width=0.9\textwidth]{figures/exp/range_legend.pdf}

	% --- 主要改动：将以下三个 subfigure 全部放在同一行 ---

	% 2. 第一部分：两张图，共用标题
	% [b]表示按底部对齐，在一行内通常比顶部对齐[t]效果好
	% 宽度从\textwidth缩小到0.32\textwidth
	\begin{subfigure}[b]{0.39\textwidth}
		\centering
		% 内部图片宽度使用\linewidth，它会自适应为容器宽度(0.32\textwidth)
		\includegraphics[width=0.495\linewidth]{figures/exp/range_multimodel.pdf}
		\hfill 
		\includegraphics[width=0.47\linewidth]{figures/exp/range_multimodel_1.pdf}
		\caption{MultiModal}
		\label{fig:range-multimodal} 
	\end{subfigure}
	\hfill % 在第一部分和第二部分之间添加弹性间距
	% 3. 第二部分：两张图，共用标题
	\begin{subfigure}[b]{0.39\textwidth}
		\centering
		\includegraphics[width=0.495\linewidth]{figures/exp/range_85.pdf}
		\hfill
		\includegraphics[width=0.47\linewidth]{figures/exp/range_71.pdf}
		\caption{Cross-Platform}
		\label{fig:range-cross-platform}
	\end{subfigure}
	\hfill % 在第二部分和第三部分之间添加弹性间距
	% 4. 第三部分：只有一张图
	\begin{subfigure}[b]{0.203\textwidth}
		\centering
		% !!! 注意：这是一个占位符，请替换成您自己的第五张图 !!!
		\includegraphics[width=0.96\linewidth]{figures/exp/range_deep100M.pdf} 
		\caption{Dig Dataset}
		\label{fig: range big dataset}
	\end{subfigure}

	% 5. 全局总标题
	\caption{\textcolor{violet}TrinityExtension——Range}
	\label{fig:TrinityExtension——Attribution_main}
\end{figure*}

	%Similar to the evaluation of \textit{Attribute Filtering} algorithms, 
	Similarly, we also evaluate \textcolor{orange}{4} key metrics mentioned above in \textit{Range Filtering} algorithms. 
%	\textcolor{orange}{For the YT-Audio dataset with synthetic attributes and the YT-Audio dataset with real attributes, we can found that the data for index construction is basically the same, indicating that the authenticity of the attribute has almost no effect on index construction.However, the WIT dataset with synthetic labels is 2048-dimensional, while the WIT-Real dataset with real labels is 512-dimensional, so the dimension will cause a big difference.}

@@

\begin{table*}[htbp]
	\caption{Algorithm Recommendation}
	\resizebox{\textwidth}{!}{
		\begin{tabular}{|l|*{16}{c|}}
			\hline
			\multirow{2}{*}{\textbf{Application Scenarios / Algorithms}} 
			& \multicolumn{6}{c|}{\textbf{AF}} 
			& \multicolumn{5}{c|}{\textbf{RF}} 
			& \multicolumn{5}{c|}{\textbf{AF / RF}} \\
			\cline{2-17}
			& \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS}  & \textbf{UNG} & \textbf{Puck} 
			& \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{Win} 
			& \textbf{ACORN}& \textbf{Faiss} & \textbf{Milvus} & \textbf{VBASE} & \textbf{PASE} \\
			\hline
			\textbf{Query Performance} & H & M & H & M &\textbf{H} & H & M & M & L & M & H & M/M & M/M & M/M & L/L & L/L \\
			\textbf{Index Time} &M  &M  &M  &M  &M  &H  &L  &M  &H  &L  &L  &L/L &\textbf{H}/ \textbf{H} &M/H  &M/M  &L/L  \\
			\textbf{Peak Memory} &L  &M  &M  &M  &M  &H  &L  &L  &M  &L  &L  &L/L  &\textbf{H}/\textbf{H}  &M/M  &H/M  &H/H \\

			\textbf{Large-Scale Dataset} & H & H & L & L &\textbf{H} &H  &M  &H  &M  &H  &\textbf{H}  &M/L  &L/M  &L/L  &M/M  &-  \\
			\textbf{Rare Attribute \& Low Range} &M  &M  &H  &H &\textbf{H}  &H  &H  &H  &L  &M  &\textbf{H} &M/M  &M/M  &L/L  &L/L  &L/L  \\
			\textbf{Robust to MultiModal Dataset} &H  &H  &L  &H  &\textbf{H}  &L  &M  &H  &M  &H  &\textbf{H}  &H/H  &M/M  &L/L  &L/L  &-/-  \\
			\textbf{Robust to Attribute Distribution} &L  &L  &H  &H  &H  &H  &-  &-  &-  &-  &-  &H/-  &L/-  &\textbf{H}/-  &L/-  &L/-  \\
			\textbf{High LID Dataset} &H  &M  &H  &M  &\textbf{H}  &M  &M  &H  &M  &H  &\textbf{H}  &L/L  &M/H  &L/L  &L/M  &L/L  \\
			\textbf{General-Purpose} &\faCheck  &\faCheck  &\faTimes  &\faTimes  &\faCheck  &\faTimes  &\faTimes  &\faCheck &\faTimes  & \faTimes &\faCheck&\faTimes  &\faCheck  &\faCheck  &\faTimes &\faTimes  \\
			\hline
		\end{tabular}
	}
	\centering
\end{table*}

>>>>

		\centering
		%	 \setlength{\abovecaptionskip}{0cm}
		%	\setlength{\belowcaptionskip}{0.1cm}
		\footnotesize{
			\begin{minipage}{\linewidth}
				\vspace{0.1cm}
				\textsuperscript{A} Post-filtering, 
				\textsuperscript{B} Pre-filtering, 
				\textsuperscript{C} Simultaneous filtering, 
				\textsuperscript{Y} Support, 
				\textsuperscript{N} Unsupport. 
				\textit{AND} and \textit{OR} indicate whether the algorithm supports the corresponding logical operations.
				\textit{Flexible Attributes} indicates whether the number of query attributes can differ from the number of attributes used during index construction. 
				\textit{Complex Boolean} indicates if the algorithm supports complex expressions, such as using the NOT operator or nested logic with parentheses.
				\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
				\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
				\textit{Disk Support} indicates whether the algorithm supports disk storage.
				\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm.
		\end{minipage}}

@@

	To investigate the performance of different attribute filtering algorithms during index construction, we evaluate \textcolor{orange}{4} key metrics in the single-attribute scenario: index construction time, index size, \textcolor{orange}{build peak memory and search peak memory}. Notably, PASE on GIST1M and Enron is omitted, as it supports only data with dimensionality less than 512.

@@

	\textit{\textbf{Index construction time.}}
	%As shown in Figure~\ref{fig:build_time_comparison_query1}, among the aforementioned 6 datasets, PASE has the longest index construction time due to its single-thread indexing support. Additionally, VBASE also supports only single-thread indexing but achieves better performance than PASE.
	 \textcolor{orange}{As shown in Figure~\ref{fig:build_time_comparison_query1}, in the above datasets, both PASE and VBASE are single-threaded indexing methods, with PASE having the longest construction time. The on-demand loading and caching strategy used by PASE results in frequent disk I/O and page scheduling, which significantly slow down the construction process. In contrast, VBASE uses full in-memory construction, leading to faster indexing.}

	For algorithms supporting 32-thread, ACORN-1 achieves the fastest index construction. This efficiency stems from its similarity to the original HNSW construction process and the use of a limited number of candidate neighbors. In contrast, ACORN-$\gamma$ incurs the highest index construction time, as it expands neighbor lists and evaluates a large candidate pool, leading to increased computational overhead. \textcolor{orange}{Its construction time on some datasets is even slower than that of the single-threaded VBASE.}

@@

	 %\underline{Faiss generates slightly smaller indexes due to its efficient index design}.

	\textit{\textbf{Build peak memory.}}
	As shown in Figure~\ref{fig:build_memory_mb_comparison}, 
	%on small-scale datasets, all methods except NHQ exhibit low memory usage. 
	\textcolor{orange}{NHQ has the highest peak memory usage on almost all datasets.}
	This is because NHQ adopts the kgraph approach for index construction, which requires loading the entire graph data into memory and maintaining a complete graph structure, leading to relatively high memory overhead.

	On large-scale datasets, CAPS exhibits slightly lower memory usage compared to other algorithms. \textcolor{orange}{The reason is that CAPS avoids redundant storage and graph structure overhead through hierarchical partitioning and AFT, and achieves a compact, sparse and controllable index. }.

	\textit{\textbf{ \textcolor{orange}{Search peak memory.}}}
	 \textcolor{orange}{As shown in Figure~\ref{fig:search_memory_mb_comparison}, we can find that the peak memory usage of each algorithm during search does not differ significantly. Among them, CAPS and NHQ have relatively higher peak memory usage, while the peak memory usage of database is comparatively lower.}

@@

		\includegraphics[width=0.95\textwidth]{figures/exp/exp_3_1.pdf}
		\caption{Effect of attribute distribution on query performance (single thread)}
		\label{fig:exp_3_1}
	\end{figure*}

	\textit{\textbf{Multi-Attribute Building and Multi-Attribute Query.}}  
	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world scenarios. To evaluate algorithm performance under this setting, we construct the index using 3 uniformly distributed attributes and apply filtering on all 3 attributes simultaneously during queries. \textcolor{violet}{In this experiment, we only evaluate algorithms that support this multi-attribute query scenario.}

	As shown in Figure~\ref{fig:exp_4_1_MultiLabel_1thread}, UNG still maintains the best performance across all datasets. Since some strong competing algorithms do not support multi-attribute querying, CAPS becomes the second-best algorithm, but its performance on small datasets is relatively poor. This is because CAPS performs multi-level partitioning based on attributes on top of the IVF index, which introduces additional overhead. While this overhead negatively impacts performance on small datasets, on large datasets, the overhead is amortized, and the increasing dataset scale makes the advantages of attribute-aware partitioning evident.

	NHQ performs moderately overall in multi-attribute joint filtering scenarios but poorly on small datasets. Its reliance on fusion distance computations makes it highly sensitive to the number of attributes, impacting both efficiency and accuracy under multi-attribute filtering.

	For IVF-based methods not specifically optimized for hybrid queries (Faiss and Milvus), their QPS shows a similar and relatively stable trend as recall varies. Among them, Milvus, as a general-purpose system, exhibits comparatively poor performance.

%	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world scenarios. To evaluate algorithm performance under this setting, we construct the index using 3 uniformly distributed attributes and apply filtering on all 3 attributes simultaneously during queries. \textcolor{orange}{Note that FilterDiskANN only supports Boolean OR logic and does not support Boolean AND. Therefore, its two Vamana-based methods are excluded from the multi-attribute construction and search experiments.}
%	%	\textcolor{red}{As Filtered-DiskANN does not support the AND rule used in our multi-attribute queries, it is excluded.}
%	%	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world application scenarios. To evaluate algorithm performance under such scenario, we construct the index using 3 uniformly distributed attributes and apply filtering conditions on all 3 attributes simultaneously during the query process.
%	
%	As shown in Figure~\ref{fig:exp_4_1_MultiLabel_1thread}, UNG achieves the best performance across all datasets. For IVF-based methods not specifically optimized for hybrid queries (Faiss\_IVF and Milvus), their QPS remains relatively stable as recall varies. Milvus, as a general-purpose system, exhibits comparatively poor performance. 
%	
%
%	The IVF-based algorithm Faiss---especially when combined with HQI\_Batch---achieves moderate performance. It naturally supports pre-filtering and remains unaffected by the increasing number of attributes. In fact, filtering can reduce the effective candidate set, thereby improving search efficiency. In contrast, the IVF-based algorithm CAPS, which is optimized for hybrid queries, employs a multi-level partitioning strategy that introduces additional overhead. This overhead negatively impacts performance on small datasets. However, on large datasets, the overhead is amortized, and the advantages of attribute-aware partitioning become evident, making CAPS the second-best performer after UNG.
%	
%	NHQ performs moderately overall but poorly on small datasets. Its reliance on fusion distance computations makes it highly sensitive to the number of attributes, impacting both efficiency and accuracy under multi-attribute filtering.

@@

	%	NHQ exhibits mediocre performance overall and performs particularly poorly on small datasets. It relies on fusion distance calculations. The fusion distance computation is highly sensitive to the number of attributes involved, thus impacting both efficiency and accuracy under multi-attribute filtering.

@@

	As illustrated in Figure~\ref{fig:exp_3_1}, the evaluated algorithms exhibit varying degrees of sensitivity to attribute distribution shifts. \textcolor{cyan}{The proximity of the 4 curves (representing different attribute distributions) in the figure reflects algorithm sensitivity to distributional variations. When the curves converge closely, the algorithm demonstrates strong resilience against attribute distribution shifts. Conversely, greater divergence among the curves indicates higher distributional dependence. Accordingly, the "Strong" label signifies robust performance consistency across varying distributions, while "Weak" denotes pronounced performance fluctuations under distributional changes.} Specifically, ACORN, Milvus, Puck, CAPS, StitchedVamana, and UNG demonstrate strong robustness to such shifts. In contrast, Faiss, FilteredVamana, NHQ, VBASE, and PASE show notable sensitivity.

@@

@@

		\hspace*{5pt}
		% 放大的图例（占满单栏）
		\includegraphics[width=0.98\columnwidth]{figures/exp/attribute_legend.pdf}

		%\vspace{0.1cm}
		\begin{subfigure}[t]{0.98\columnwidth}
		\centering
		% First plot for the shared subfigure
		\includegraphics[width=0.507\linewidth]{figures/exp/attribute_multimodel.pdf}
		\hfill % Pushes the two plots apart
		% Second plot for the shared subfigure
		\includegraphics[width=0.48\linewidth]{figures/exp/attribute_multimodel_1.pdf}

		% Shared caption for the two plots above
		\captionsetup{font=small}
		\caption{MultiModal}
		\label{fig:MultiModal} % A single label for the combined subfigure
		\end{subfigure}

		\begin{subfigure}[t]{0.507\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/exp/attribute_85.pdf}
			\caption{\footnotesize Different Computer}
			\label{fig:Different Computer}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.48\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/exp/attribute_100M.pdf}
			\caption{\footnotesize Big Dataset}
			\label{fig:Big Dataset}
		\end{subfigure}

		\caption{\textcolor{violet}TrinityExtension——Attribution}
		\label{fig:TrinityExtension——Attribution}
	\end{figure}

@@

		\hspace*{5pt}
		% 放大的图例（占满单栏）
		\includegraphics[width=0.98\columnwidth]{figures/indexData/rangeFilter_legend_only.pdf}

		%\vspace{0.1cm}

		% 三图横排
		\begin{subfigure}[t]{0.495\columnwidth}
			\centering
			\captionsetup{font=small}
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_build_time_comparison_query.pdf}
			\caption{\footnotesize Construction time}
			\label{fig:rangeFilter_build_time}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.495\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_index_size_mb_comparison_query.pdf}
			\caption{\footnotesize Index size}
			\label{fig:rangeFilter_index_size_mb}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.495\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_memory_mb_comparison_query.pdf}
			\caption{\footnotesize Build peak memory}
			\label{fig:rangeFilter_build_memory_mb}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.495\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/searchMem/range_memory_comparison.pdf}
			\caption{\footnotesize Search peak memory}
			\label{fig:rangeFilter_search_memory_mb}
		\end{subfigure}

		%		\caption{Time and space overhead of range filtering index construction}
%		\caption{Time and space overhead of index construction}
		\caption{\textcolor{violet}{Time and space overhead}}
		\label{fig:rangeFilter_build_index_comparison}
	\end{figure}

	%Similar to the evaluation of \textit{Attribute Filtering} algorithms, 
	Similarly, we also evaluate \textcolor{orange}{4} key metrics mentioned above in \textit{Range Filtering} algorithms. \textcolor{orange}{For the YT-Audio dataset with synthetic attributes and the YT-Audio dataset with real attributes, we can found that the data for index construction is basically the same, indicating that the authenticity of the attribute has almost no effect on index construction.
	However, the WIT dataset with synthetic labels is 2048-dimensional, while the WIT-Real dataset with real labels is 512-dimensional, so the dimension will cause a big difference.}

@@

\begin{table*}[htbp]
	\caption{Algorithm Recommendation}
	\resizebox{\textwidth}{!}{
		\begin{tabular}{|l|*{16}{c|}}
			\hline
			\multirow{2}{*}{\textbf{Application Scenarios / Algorithms}} 
			& \multicolumn{6}{c|}{\textbf{AF}} 
			& \multicolumn{5}{c|}{\textbf{RF}} 
			& \multicolumn{5}{c|}{\textbf{AF / RF}} \\
			\cline{2-17}
			& \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS}  & \textbf{UNG} & \textbf{Puck} 
			& \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{Win} 
			& \textbf{ACORN}& \textbf{Faiss} & \textbf{Milvus} & \textbf{VBASE} & \textbf{PASE} \\
			\hline
			\textbf{Query Performance} & H & M & H & M &\textbf{ H} & H & M & M & L & M & H & M/M & M/M & M/M & L/L & L/L \\
			\textbf{Index Time} &M  &M  &M  &M  &M  &H  &L  &M  &H  &L  &L  &L/L &\textbf{H}/ \textbf{H} &M/H  &M/M  &L/L  \\
			\textbf{Peak Memory} &L  &M  &M  &M  &M  &H  &L  &L  &M  &L  &L  &L/L  &\textbf{H}/\textbf{H}  &M/M  &H/M  &H/H \\

			\textbf{Large-Scale Dataset} & H & H & L & L &\textbf{H } &H  &M  &H  &M  &H  &\textbf{H}  &M/L  &L/M  &L/L  &M/M  &-  \\
			\textbf{Rare Attribute \& Low Range} &M  &M  &H  &H &\textbf{H}  &H  &H  &H  &L  &M  &\textbf{H} &M/M  &M/M  &L/L  &L/L  &L/L  \\
			\textbf{Insensitive to Data Distribution} &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\
			\textbf{High LID Dataset} &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\
			\textbf{General-Purpose} &\faCheck  &\faCheck  &\faTimes  &\faTimes  &\faCheck  &\faTimes  &\faTimes  &\faCheck &\faTimes  & \faTimes &\faCheck&\faTimes  &\faCheck  &\faCheck  &\faTimes &\faTimes  \\
			\hline
		\end{tabular}
	}
	\centering
\end{table*}
